Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-09 paper.tex
Import.
iter

\textbf{Transformers.} Since it is common to modify or filter data before
feeding it to a learning algorithm, some estimators in the library implement a
\textit{transformer} interface which defines a \texttt{transform} method. It
takes as input some new data \texttt{X\_test} and yields as output a transformed
version of \texttt{X\_test} Preprocessing, feature selection and dimensionality
reduction algorithms are all provided as transformers within the library.  In
our example, if one wanted to preprocess the inputs \texttt{X\_train} before
fitting the logistic regression estimator, e.g., by standardizing the feature
values, one could thus simply write:
\begin{verbatim}
scaler = StandardScaler()
scaler.fit(X_train)
X_train = scaler.transform(X_train)
\end{verbatim}
Of course, in practice, it is important to apply the same preprocessing to the
test data \texttt{X\_test}. This can easily be done as follows:
\begin{verbatim}
X_test = scaler.transform(X_test)
\end{verbatim}

@@

In \textit{scikit-learn}, the \texttt{fit} method always returns the estimator
it was called on, hence making method chaining possible.  Using this technique,
we can thus rewrite the \texttt{StandardScaler} example above in a single line:
\begin{verbatim} 
X_train = StandardScaler().fit(X_train).transform(X_train)
\end{verbatim} 
In \textit{scikit-learn}, \texttt{fit(X\_train).transform(X\_train)} can further
be rewritten as \texttt{fit\_transform(X\_train)}.  Combining the \texttt{fit}
and \texttt{transform} methods into a single method \texttt{fit\_transform}
allows to share computations, which often makes a huge difference in practice.
In the same spirit, \textit{scikit-learn} sometimes provides the
\texttt{fit\_predict} method for combining the \texttt{fit} and \texttt{predict}
methods. This is especially useful for retrieving cluster predictions with
respect to the training data \texttt{X\_train} in clustering algorithms.

@@

SciPy's handling of sparse matrices is one source of confusion
for scikit-learn developers and users alike.
The \texttt{scipy.sparse} package offers quite full-featured support
for this kind of data structure,
which is crucial to achieving performance and scalability
in the face of high-dimensional inputs
(including, but not limited to, NLP applications).
However, the interface exposed by its classes
deviates from the NumPy array interface, sometimes subtly so,
sometimes entirely.  % XXX is this grammatically correct?
For example, while NumPy arrays have a variable number of dimensions,
so that vectors can be considered 1-d arrays
(without a distinction between row and column vectors),
matrices are 2-d, etc., \texttt{scipy.sparse} matrices are always 2-dimensional,
meaning that special care has to be taken when handling sparse vectors.

>>>>

\textbf{Transformers.} Since it is common to modify or filter data before
feeding it to a learning algorithm, some estimators in the library implement a
\textit{transformer} interface which defines a \texttt{transform} method. It
takes as input some new data \texttt{X\_test} and yields as output a transformed
version of \texttt{X\_test} Preprocessing, feature selection and dimensionality
reduction algorithms are all provided as transformers within the library.  In
our example, if one wanted to preprocess the inputs \texttt{X\_train} before
fitting the logistic regression estimator, e.g., by standardizing the feature
values, one could thus simply write:
\begin{verbatim}
from sklearn.preprocessing import StandardScaler
scaler = StandardScaler()
scaler.fit(X_train)
X_train = scaler.transform(X_train)
\end{verbatim}
Of course, in practice, it is important to apply the same preprocessing to the
test data \texttt{X\_test}. This can easily be done as follows:
\begin{verbatim}
X_test = scaler.transform(X_test)
\end{verbatim}
Transformers also include a variety of learning algorithms, such as
dimension reduction (PCA, manifold learning techniques), Kernel
approximation techniques, and any other approach that can be used to
derive a modified representation of the data.

@@

In \textit{scikit-learn}, the \texttt{fit} method always returns the estimator
it was called on, hence making method chaining possible.  Using this technique,
we can thus rewrite the \texttt{StandardScaler} example above in a single line:
\begin{verbatim} 
X_train = StandardScaler().fit(X_train).transform(X_train)
\end{verbatim} 
In addition, \texttt{fit(X\_train).transform(X\_train)} can further
be rewritten as \texttt{fit\_transform(X\_train)}.  Combining the \texttt{fit}
and \texttt{transform} methods into a single method \texttt{fit\_transform}
allows to share computations, which often makes a huge difference in practice.
In the same spirit, \textit{scikit-learn} sometimes provides the
\texttt{fit\_predict} method for combining the \texttt{fit} and \texttt{predict}
methods. This is especially useful for retrieving cluster predictions with
respect to the training data \texttt{X\_train} in clustering algorithms.

@@

SciPy's handling of sparse matrices is one source of confusion
for scikit-learn developers and users alike.
The \texttt{scipy.sparse} package offers support
for this kind of data structure,
which is crucial to achieving performance and scalability
in the face of high-dimensional inputs
(including, but not limited to, NLP applications).
However, the interface exposed by its classes
deviates from the NumPy array interface, sometimes subtly so,
sometimes entirely.  % XXX is this grammatically correct?
For example, while NumPy arrays have a variable number of dimensions,
so that vectors can be considered 1-d arrays
(without a distinction between row and column vectors),
matrices are 2-d, etc., \texttt{scipy.sparse} matrices are always 2-dimensional,
meaning that special care has to be taken when handling sparse vectors.
